Comparison of Three Anonymization Tools for a Health Fitness Study

### 2025-08-08 submission_materials/aug25/article.tex
update for August 25 submission

The public repository at\mycite{18} contains all of the anonymized data used for this paper. This anonymized data may be used for the purpose of studying anonymity, either by sharing the data or by running the anonymization software locally. Note that the original pseudonymized data from which the anonymized data was derived is considered personal data and is therefore not publicly available.  \hl{Please contact Bojan Leskosek (bojan.Leskosek@fsp.uni-lj.si) or Gregor Jurak (gregor.jurak@fsp.uni-lj.si) to access the original dataset. Any data access request should state the purpose for requesting the data, describe measures how sensitive data will be protected and assurance of ethical use. Requesters need to sign a Data Use Agreement (DUA). We guarantee that reasonable requests will be honored. }

>>>>

The public repository at \mycite{18} contains all of the anonymized data used for this paper. This anonymized data may be used and shared freely for the purpose of studying anonymity. Note that the original pseudonymized data from which the anonymized data was derived is personal data and is therefore not publicly available. Please contact Bojan Leskosek (bojan.Leskosek@fsp.uni-lj.si) or Gregor Jurak (gregor.jurak@fsp.uni-lj.si) to access the original dataset. Requesters need to sign a Data Use Agreement (DUA), which is available at \mycite{18}. The DUA requires the the requester state the research purpose, and to agree to protect the data, to not share the data, and to destroy it upon completion of the research. All legitimate requests will be honored.
